Turbulence in compact to giant H~II regions

### 2022-12-19 strucfunc_paper.tex
Finish the acknowledgments

@@

Based on observations made with KPNO telescopes
\textit{complete KPNO acknowledgment}.
Based on observations made with ESO Telescopes at the La Silla Paranal Observatory under programme IDs 076.C-0888 and 098.D-0211.
Based on observations made as part of the Gaia-ESO Spectroscopic Survey
\textit{complete Gaia-ESO acknowledgment}.
Based on observations made with the WHT
\textit{complete WHT acknowledgment}.
We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments for 30 Doradus derived from MUSE-VLT observations.
JGV acknowledges and thanks CONACyT-Mexico for the PhD research scholarship.

>>>>

\usepackage[spanish,es-minimal,english]{babel}

@@

Based in part on observations obtained at the Kitt Peak National Observatory,
which is operated by the Association of Universities for Research in Astronomy, Inc.,
under cooperative agreement with the National Science Foundation.
Based in part on observations made with the MUSE and FLAMES spectrographs
on VLT telescopes at the La Silla Paranal Observatory, ESO, Chile
under programme IDs 188.B-3002, 076.C-0888 and 098.D-0211.
Based in part on observations made with the William Herschel Telescope
operated by the Isaac Newton Group of Telescopes,
located at the Spanish
\foreignlanguage{spanish}{Roque de los Muchachos}
Observatory of the
\foreignlanguage{spanish}{Instituto de Astrofisica de Canarias}
on the island of La Palma. 
We gratefully acknowledge financial support provided by
\foreignlanguage{spanish}{%
  Dirección General de Asuntos del Personal Académico,
  Universidad Nacional Autónoma de México},
through grant
\foreignlanguage{spanish}{%
  Programa de Apoyo a Proyectos de Investigación
  e Inovación Tecnológica}
IN109823.  
We are grateful to Norberto Castro Rodríguez for providing maps of emission line velocity moments
for 30~Doradus derived from MUSE-VLT observations.
JGV acknowledges and thanks CONACyT-Mexico for a PhD research scholarship.
